06_DESeqALL

### 2019-12-20 analysis/06_DESeq2_ALL.Rmd
patial new hyp

char <- plot_grid(
          b + theme(axis.title.x = element_blank(), axis.text.x = element_blank()),
          c + theme(axis.title = element_blank(), axis.text = element_blank()) ,
          d + theme(axis.title = element_blank(), axis.text = element_blank()), 
          f + theme(axis.title = element_blank(), axis.text = element_blank()),
          g + theme(axis.title = element_blank(), axis.text = element_blank()),
          h + theme(axis.title = element_blank(), axis.text = element_blank()),
          i + theme(axis.title = element_blank(), axis.text = element_blank()),
          nrow = 1, rel_widths = c(1.1,1,1,1,1,1,1))

remove <- plot_grid( 
          a + theme(axis.title.x = element_blank(), axis.text.x = element_blank()),
          NULL, 
          j + theme(axis.title = element_blank(), axis.text = element_blank()) , 
          k + theme(axis.title = element_blank(), axis.text = element_blank()) , 
          l + theme(axis.title = element_blank(), axis.text = element_blank()) , 
          m + theme(axis.title = element_blank(), axis.text = element_blank()), 
          NULL, nrow = 1, rel_widths = c(1.1, 0.5, 1,1,1,1,0.5))

timing <- plot_grid( 
          n , 
          o + theme(axis.title.y = element_blank(), axis.text.y = element_blank()) , 
          NULL,
          p + theme(axis.title.y = element_blank(), axis.text.y = element_blank()), 
          q + theme(axis.title.y = element_blank(), axis.text.y = element_blank())+
            labs(x = "Log fold change, pituitary") , 
           NULL,
          r + theme(axis.title.y = element_blank(), axis.text.y = element_blank()) , 
          s + theme(axis.title.y = element_blank(), axis.text.y = element_blank()),
            nrow = 1, rel_widths = c(1.1,1, 0.5, 1,1,0.5, 1,1))

>>>>

char <- plot_grid(
          b + theme(axis.title.x = element_blank(), axis.text.x = element_blank()),
          c + theme(axis.title = element_blank(), axis.text = element_blank()) ,
          d + theme(axis.title = element_blank(), axis.text = element_blank()), 
          f + theme(axis.title = element_blank(), axis.text = element_blank()),
          g + theme(axis.title = element_blank(), axis.text = element_blank()),
          h + theme(axis.title = element_blank(), axis.text = element_blank()),
          i + theme(axis.title = element_blank(), axis.text = element_blank()),
          nrow = 1, rel_widths = c(1.2,1,1,1,1,1,1))

remove <- plot_grid( 
          a + theme(axis.title.x = element_blank(), axis.text.x = element_blank()),
          NULL, 
          j + theme(axis.title = element_blank(), axis.text = element_blank()) , 
          k + theme(axis.title = element_blank(), axis.text = element_blank()) , 
          l + theme(axis.title = element_blank(), axis.text = element_blank()) , 
          m + theme(axis.title = element_blank(), axis.text = element_blank()), 
          NULL, nrow = 1, rel_widths = c(1.2, 1, 1,1,1,1,1))

timing <- plot_grid( 
          n , 
          o + theme(axis.title.y = element_blank(), axis.text.y = element_blank()) , 
          NULL,
          p + theme(axis.title.y = element_blank(), axis.text.y = element_blank()), 
          q + theme(axis.title.y = element_blank(), axis.text.y = element_blank())+
            labs(x = "Log fold change, pituitary") , 
           NULL,
          r + theme(axis.title.y = element_blank(), axis.text.y = element_blank()) , 
          s + theme(axis.title.y = element_blank(), axis.text.y = element_blank()),
            nrow = 1, rel_widths = c(1.2,1, 0.5, 1,1,0.5, 1,1))

### 2019-12-20 analysis/06c_DESeq2_ALL_hypothalamus.Rmd
better gonad and hypothalamus figures
patial new hyp

@@

```{r  eval=T}
n5.extend <- createDEGdfsave(dds.hypothalamus, "treatment", "extend", "n5", "hypothalamus")
```

```{r volcanos-hyp, fig.width=7, fig.height=3.5}
a <- plot.volcano(inc.d3.m.inc.d3 , "treatment",   "m.inc.d3", "inc.d3",   colorsvolcano)  
b <- plot.volcano(inc.d9.m.inc.d9, "treatment",  "m.inc.d9", "inc.d9" , colorsvolcano) 
c <- plot.volcano(inc.d17.m.inc.d17 , "treatment",  "m.inc.d17", "inc.d17" , colorsvolcano) 
d <- plot.volcano(hatch.m.n2 , "treatment",   "m.n2", "hatch", colorsvolcano)

e <- plot.volcano(inc.d9.m.inc.d8 , "treatment",   "m.inc.d8", "inc.d9"  , colorsvolcano) 
f <- plot.volcano(hatch.m.inc.d8 , "treatment",    "hatch", "m.inc.d8"  , colorsvolcano)

g <- plot.volcano(inc.d17.prolong , "treatment",   "prolong", "inc.d17",  colorsvolcano)  
h <- plot.volcano(hatch.prolong , "treatment",  "hatch", "prolong", colorsvolcano)

i <- plot.volcano(hatch.extend , "treatment",  "extend", "hatch" , colorsvolcano)  
j <- plot.volcano(n5.extend , "treatment",  "extend", "n5", colorsvolcano)

remove <- plot_grid(a + labs(y = "hypothalamus -log10(p-value)"),
          b + theme(axis.title.y = element_blank(), axis.text.y = element_blank()),
          c + theme(axis.title.y = element_blank(), axis.text.y = element_blank()) ,
          d + theme(axis.title.y = element_blank(), axis.text.y = element_blank()), 
          nrow = 1, rel_widths = c(1.2,1,1,1),
          labels = c("a","b","c","d"), label_size = 9)
remove

timing <- plot_grid(e +  labs(y = "hypothalamus -log10(p-value)"),
          f + theme(axis.title.y = element_blank(), axis.text.y = element_blank()),
          g + theme(axis.title.y = element_blank(), axis.text.y = element_blank()),
          h + theme(axis.title.y = element_blank(), axis.text.y = element_blank()),
          i + theme(axis.title.y = element_blank(), axis.text.y = element_blank()) , 
          j + theme(axis.title.y = element_blank(), axis.text.y = element_blank()) , 
          nrow = 1, rel_widths = c(1.2,1,1,1,1,1),
          labels = c("a","b","c", "d","e","f"), label_size = 9)
timing
```

>>>>

```{r eval=T}
control.bldg <- createDEGdfsave(dds.hypothalamus, "treatment", "bldg", "control", "hypothalamus")
```

```{r  eval=T}
bldg.lay <- createDEGdfsave(dds.hypothalamus, "treatment", "lay", "bldg", "hypothalamus")
```

```{r  eval=T}
lay.inc.d3 <- createDEGdfsave(dds.hypothalamus, "treatment", "inc.d3", "lay", "hypothalamus") 
```

```{r  eval=T}
inc.d3.inc.d9 <- createDEGdfsave(dds.hypothalamus,  "treatment", "inc.d9", "inc.d3", "hypothalamus") 
```

```{r  eval=T}
inc.d9.inc.d17 <- createDEGdfsave(dds.hypothalamus, "treatment", "inc.d17", "inc.d9", "hypothalamus")
```

```{r  eval=T}
inc.d17.hatch <- createDEGdfsave(dds.hypothalamus, "treatment", "hatch", "inc.d17", "hypothalamus") 
```

```{r  eval=T}
hatch.n5 <- createDEGdfsave(dds.hypothalamus, "treatment", "n5", "hatch", "hypothalamus") 
```

```{r  eval=T}
n5.n9 <- createDEGdfsave(dds.hypothalamus, "treatment", "n9", "n5", "hypothalamus") 
```

@@

```{r  eval=T}
n5.extend <- createDEGdfsave(dds.hypothalamus, "treatment", "n5", "extend", "hypothalamus")
```

```{r eval=T}
sex <- createDEGdfsave(dds.hypothalamus, "sex", "male", "female", "hypothalamus") 
```

```{r volcanos-hypothalamus, fig.height= 6, fig.width=6}
a <- plot.volcano(sex, "sex", "male", "female", colorsvolcano)
b <- plot.volcano(control.bldg, "treatment", "bldg", "control", colorsvolcano)
c <- plot.volcano(bldg.lay, "treatment", "lay", "bldg", colorsvolcano)
d <- plot.volcano(lay.inc.d3, "treatment", "inc.d3", "lay", colorsvolcano) 
e <- plot.volcano(inc.d3.inc.d9, "treatment", "inc.d9", "inc.d3", colorsvolcano) 
f <- plot.volcano(inc.d9.inc.d17, "treatment", "inc.d17", "inc.d9", colorsvolcano)
g <- plot.volcano(inc.d17.hatch, "treatment", "hatch", "inc.d17", colorsvolcano) 
h <- plot.volcano(hatch.n5, "treatment", "n5", "hatch", colorsvolcano) 
i <- plot.volcano(n5.n9, "treatment", "n9", "n5", colorsvolcano)

j <- plot.volcano(inc.d3.m.inc.d3 , "treatment",   "m.inc.d3", "inc.d3",   colorsvolcano)  
k <- plot.volcano(inc.d9.m.inc.d9, "treatment",  "m.inc.d9", "inc.d9" , colorsvolcano) 
l <- plot.volcano(inc.d17.m.inc.d17 , "treatment",  "m.inc.d17", "inc.d17" , colorsvolcano) 
m <- plot.volcano(hatch.m.n2 , "treatment",   "m.n2", "hatch", colorsvolcano)

n <- plot.volcano(inc.d9.m.inc.d8 , "treatment",   "m.inc.d8", "inc.d9"  , colorsvolcano) 
o <- plot.volcano(hatch.m.inc.d8 , "treatment",    "hatch", "m.inc.d8"  , colorsvolcano)  
p <- plot.volcano(inc.d17.prolong , "treatment",   "prolong", "inc.d17",  colorsvolcano)  
q <- plot.volcano(hatch.prolong , "treatment",  "hatch", "prolong", colorsvolcano) 
r <- plot.volcano(hatch.extend , "treatment",  "extend", "hatch" , colorsvolcano)  
s <- plot.volcano(n5.extend , "treatment",  "extend", "n5", colorsvolcano)

char <- plot_grid(
          b + theme(axis.title.x = element_blank(), axis.text.x = element_blank()),
          c + theme(axis.title = element_blank(), axis.text = element_blank()) ,
          d + theme(axis.title = element_blank(), axis.text = element_blank()), 
          f + theme(axis.title = element_blank(), axis.text = element_blank()),
          g + theme(axis.title = element_blank(), axis.text = element_blank()),
          h + theme(axis.title = element_blank(), axis.text = element_blank()),
          i + theme(axis.title = element_blank(), axis.text = element_blank()),
          nrow = 1, rel_widths = c(1.2,1,1,1,1,1,1))

remove <- plot_grid( 
          a + theme(axis.title.x = element_blank(), axis.text.x = element_blank()),
          NULL, 
          j + theme(axis.title = element_blank(), axis.text = element_blank()) , 
          k + theme(axis.title = element_blank(), axis.text = element_blank()) , 
          l + theme(axis.title = element_blank(), axis.text = element_blank()) , 
          m + theme(axis.title = element_blank(), axis.text = element_blank()), 
          NULL, nrow = 1, rel_widths = c(1.2, 1, 1,1,1,1,1))

timing <- plot_grid( 
          n , 
          o + theme(axis.title.y = element_blank(), axis.text.y = element_blank()) , 
          NULL,
          p + theme(axis.title.y = element_blank(), axis.text.y = element_blank()), 
          q + theme(axis.title.y = element_blank(), axis.text.y = element_blank())+
            labs(x = "Log fold change, pituitary") , 
           NULL,
          r + theme(axis.title.y = element_blank(), axis.text.y = element_blank()) , 
          s + theme(axis.title.y = element_blank(), axis.text.y = element_blank()),
            nrow = 1, rel_widths = c(1.2,1, 0.5, 1,1,0.5, 1,1))

charicons <- png::readPNG("../figures/images/DoveParentsRNAseq_volcanos-char.png")
charicons <-  grid::rasterGrob(charicons, interpolate=TRUE)

removeicons <- png::readPNG("../figures/images/DoveParentsRNAseq_volcanos-removal.png")
removeicons <-  grid::rasterGrob(removeicons, interpolate=TRUE)

timingicons <- png::readPNG("../figures/images/DoveParentsRNAseq_volcanos-timing.png")
timingicons <-  grid::rasterGrob(timingicons, interpolate=TRUE)

plot_grid(charicons, char, removeicons, remove, timingicons, timing, nrow = 6, rel_heights = c(0.9,1,0.9,1,0.9,1.2))
```
